### 2022-01-07 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_neutral_landscapes_jl@bda89e4da88d5b6854a5b28b5327f7914790a718 🚀
Deploying to gh-pages from @ gottacatchenall/ms_neutral_landscapes_jl@e2a240feba5ca8d423db8b5bb2a9afc549c7f19a 🚀

The two primary packages used to simulate neutral landscapes are
\texttt{NLMR} in (the \texttt{R} language) (Sciaini \emph{et al.} 2018)
and \texttt{NLMpy} (in Python; Etherington \emph{et al.} 2015). We
present \texttt{NeutralLandscapes.jl}, a package in \texttt{Julia} for
neutral landscapes which is faster than both above package. Here we
demonstrate that \texttt{NeutralLandscapes.jl}, depending on the method,
is orders of magnitude faster than previous neutral landscape packages.
As biodiversity science becomes increasingly concerned with temporal
change and its consequences, its clear there is a gap in methodology in
generating neutral landscapes that change over time. In addition we
present a novel method for generating landscape change with prescribed
levels of spatial and temporal autocorrelation, which is implemented in
\texttt{NeutralLandscapes.jl}

@@

plot(
    heatmap(rand(MidpointDisplacement(0.8), size(layer), mask=qcmask); pltsettings),
    heatmap(rand(PlanarGradient(), size(layer), mask=qcmask); pltsettings),
    heatmap(rand(PerlinNoise((4,4)), size(layer), mask=qcmask); pltsettings),
    heatmap(rand(NearestNeighborCluster(0.5), size(layer), mask=qcmask); pltsettings),
    dpi=400
)

savefig("interoperable.png")
\end{verbatim}

>>>>

We present \texttt{NeutralLandscapes.jl}, a package in \texttt{Julia}
for neutral landscapes. The two primary packages used to simulate
neutral landscapes are \texttt{NLMR} in (the \texttt{R} language)
(Sciaini \emph{et al.} 2018) and \texttt{NLMpy} (in Python; Etherington
\emph{et al.} 2015). Here we demonstrate that
\texttt{NeutralLandscapes.jl}, depending on the method, is orders of
magnitude faster than previous neutral landscape packages.

As biodiversity science becomes increasingly concerned with temporal
change and its consequences, its clear there is a gap in methodology in
generating neutral landscapes that change over time. In addition we
present a novel method for generating landscape change with prescribed
levels of spatial and temporal autocorrelation, which is implemented in
\texttt{NeutralLandscapes.jl}

@@

plot(
    heatmap(rand(MidpointDisplacement(0.8), size(layer), mask=qcmask); pltsettings),
    heatmap(rand(PlanarGradient(), size(layer), mask=qcmask); pltsettings),
    heatmap(rand(PerlinNoise((4,4)), size(layer), mask=qcmask); pltsettings),
    heatmap(rand(NearestNeighborCluster(0.5), size(layer), mask=qcmask); pltsettings),
    dpi=400
)
\end{verbatim}
